### 2018-06-06 FrascatiPlot/Paper/NucleiB2.tex
adding a reminder to mention also the Braaten paper
Alexander starts doing some minor fixes

\subsection{Full coalescence}{sec:coalescence}
In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}. \textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

@@

\subsection{(Anti-)nuclei with $A$ = 2, 3, 4}
\subsection{(Anti-)hyper-nuclei}
- cite Che Ming Ko \cite{Zhang:2018euf} 
\section{Projections for the LHC Run 3 and 4}\label{sec:projections}

>>>>

\subsection{Full coalescence}
\label{subsec:FullCoalescence}

In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}. \textcolor{red}{Consider mentioning the approximations done by Uli in his paper, if there is time and how Uli's paper relates to the Wigner formalism.}
In this approach, the quantum mechanical nature of the coalescence products is explicitly accounted for by means of an average quantum mechanical correction factor, $\langle C_{A} \rangle$. In the case of the deuteron, the quantum mechanical correction factor $\langle C_{d} \rangle$ has been approximated as

@@

\subsection{(Anti-)nuclei with $A$ = 2, 3, 4}
\subsection{(Anti-)hyper-nuclei}
- cite Che Ming Ko \cite{Zhang:2018euf}

\subsection{Other exotic QCD objects}

We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature. One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de

\section{Projections for the LHC Run 3 and 4}\label{sec:projections}
